Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-15 reportTII-ArticleHIL.tex
Fixed Fig. 13: MIMO system block diagram

 \begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](plant){};

    % Connections
	\draw[stealth-,thick]
    (plant.145)--node[very near end,above](in1){Input 1}++(-1.9,0);    
    \draw[stealth-,thick]
    (plant.180)--node[very near end,above](in2){Input 2}++(-1.9,0);
    %\draw[ultra thick,Dotted] (in2) -- (inn);
    \draw[-stealth,thick]
    (plant.-145)--node[very near end,above](inn){Input n}++(1.9,0);

    \draw[-stealth,thick]
    (plant.30)--node[very near end,above](out1){Output 1}++(1.9,0);
    \draw[-stealth,thick]
    (plant.0)--node[very near end,above](out2){Output 2}++(1.9,0);
    %\draw[ultra thick,Dotted] (out2) -- (outm);
    \draw[-stealth,thick]
    (plant.-30)--node[very near end,above](outm){Output m}++(1.9,0);
  \end{tikzpicture}
    \caption{Multiple Input Multiple Output Dynamic System Block Diagram}
    \label{fig:mimoDynamicBlockDiagram}
 \end{figure}

>>>>

 \begin{figure}[htbp]
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](plant){MIMO system};

    % Connections
	\draw[stealth-,thick]
  (plant.150)--++(-1.2,0)node[left](in1){$x_1$};    
    \draw[stealth-,thick]
    (plant.170)--++(-1.2,0)node[left](in2){$x_2$};
    \draw
    ($(plant.180)+(-0.5,0)$)node[yshift=-0.9mm]{$\vdots$};
    \draw[stealth-,thick]
    (plant.-150)--++(-1.2,0)node[left](inn){$x_n$};

    \draw[-stealth,thick]
    (plant.30)--++(1.2,0)node[right](out1){$y_1$};
    \draw[-stealth,thick]
    (plant.10)--++(1.2,0)node[right](out2){$y_2$};
    \draw
    ($(plant.0)+(0.5,0)$)node[yshift=-0.9mm]{$\vdots$};
    \draw[-stealth,thick]
    (plant.-30)--++(1.2,0)node[right](outm){$y_m$};
  \end{tikzpicture}
    \caption{Multiple Input Multiple Output Dynamic System Block Diagram}
    \label{fig:mimoDynamicBlockDiagram}
 \end{figure}
